Capabilities, MMIO and Robust Safety

### 2020-04-03 capability-notes/driver-notes/main.tex
tweak

The capability $(\X{E}, g, b, e, a_i)$ then represents a closure for this same piece
of code. Adversarial code only gets access to the closure (as an enter
capability), in order to avoid them from executing or reading arbitrary lines of
code within the trusted module.

Notice the universal quantification over worlds in the precondition;
this needs to be there, since we do not know in what world our code will be
called.
%
\rk{toplevel:ocpl_explicit_worlds}

The theorem above is \emph{incomplete}. In other words, it is not provable as
is, because it includes no notion of adversarial context (similar to OCPL's
\textit{AdvCtx}), and therefore imposes no restriction on the adversarial code
(i.e., the contents of the $r$ and $m$ other than our verified code).
%
As such, the statement can be trivially falsified by taking an attacker with
direct read or write access to any location in \MMIO, or with direct access to
the trusted code's internal state.

>>>>

The capability $(\X{E}, g, b, e, a_i)$ then represents a closure for this same
piece of code. Adversarial code should only get access to the closure (as an
enter capability), in order to prevent it from executing or reading arbitrary
lines of code within the trusted module.

Notice that we also need to provide a world to instantiate the expression
relation, here, we universally quantify over it...
%
\rk{toplevel:ocpl_explicit_worlds}

\bigskip

The theorem above is \emph{incomplete}. In particular, it is not provable as
is, because it includes no notion of adversarial context (similar to OCPL's
\textit{AdvCtx}), and therefore imposes no restriction on the adversarial code
(i.e., the contents of the $r$ and $m$ other than our verified code).
%
As such, the statement can be trivially falsified by taking an attacker with
direct read or write access to any location in \MMIO, or with direct access to
the trusted code's internal state.
